### 2019-10-11 paper/introduction.tex
introduction & method
Abstract, introduction & method after Andrei's revision

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation
nuclear systems. These goals are: safety and reliability, economics,
sustainability, non-proliferation and physical protection
\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows transferring fission heat from reactor
core to heat exchanger.

@@

Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU)
\cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
heuer2014towards,fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF
\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
\begin{itemize}
	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay 
	tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. 
	\cite{betzler2016modeling}.
	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or 
	part of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section 2. 
Methodology and tools is descried in section 3. Extraction and feed mechanisms 
are addressed in section 4. Section 5 focuses on the results and discussion. 
Finally, section 6 highlights the conclusions.

@@

% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation
nuclear systems. These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows transferring fission heat from reactor
core to heat exchanger.

@@

Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
heuer2014towards,fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:

\begin{itemize}
	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30. We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This present paper is organized as follows: after an introduction about 
\gls{MSR} systems, the model description is discussed in section 2. 
Methodology and tools is descried in section 3. Extraction and feed mechanisms 
are addressed in section 4. Section 5 focuses on the results and discussion. 
Finally, section 6 highlights the conclusions.

@@
